Cross Validation Analysis

### 2023-05-17 minos/validation/cross_validation.Rmd
Fixed typo in the cross-validation notebook, and updated the util function combine_and_pivot() to remove all missing values (negative 1-3, 7-9). Also removed some .pngs that were tracked by accident
Added a variable for the save.path in cross_validation.Rmd so it only has to be changed in one place

# cv simulation pop (not used for transitions)
cv.simul.files <- list.files('Minos/data/final_US/cross_validation/simulation/',
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw <- do.call(rbind, lapply(cv.simul.files, read.csv))
```

@@

plot_mean_comparison(pivoted.df = income.pivoted, 
                     var = 'hh_income', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

@@

plot_mean_comparison(pivoted.df = sf12.m.pivoted, 
                     var = 'SF_12_MCS', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

@@

plot_mean_comparison(pivoted.df = sf12.p.pivoted, 
                     var = 'SF_12_PCS', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

@@

```{r}
yearly_box_plots(pivoted.df = sf12.p.pivoted,
                 var = 'nutrition_quality',
                 scen1 = 'raw',
                 scen2 = 'simulation')
```

@@

plot_mean_comparison(pivoted.df = nut.pivoted, 
                     var = 'nutrition_quality', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

@@

plot_mean_comparison(pivoted.df = tobacco.pivoted, 
                     var = 'ncigs', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')

@@

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'housing_quality',
                 save = TRUE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

@@

cv_ordinal_plots(pivoted.df = nhsafe.pivoted, 
                 var = 'neighbourhood_safety',
                 save = TRUE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

@@

cv_ordinal_plots(pivoted.df = lnly.pivoted, 
                 var = 'loneliness',
                 save = TRUE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

>>>>

# cv simulation pop (not used for transitions)
cv.simul.files <- list.files('Minos/data/final_US/cross_validation/simulation/',
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw <- do.call(rbind, lapply(cv.simul.files, read.csv))

savepath <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/'
```

@@

plot_mean_comparison(pivoted.df = income.pivoted, 
                     var = 'hh_income', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = savepath)

@@

plot_mean_comparison(pivoted.df = sf12.m.pivoted, 
                     var = 'SF_12_MCS', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = savepath)

@@

plot_mean_comparison(pivoted.df = sf12.p.pivoted, 
                     var = 'SF_12_PCS', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = savepath)

@@

```{r}
yearly_box_plots(pivoted.df = sf12.p.pivoted,
                 var = 'SF_12_PCS',
                 scen1 = 'raw',
                 scen2 = 'simulation')
```

@@

plot_mean_comparison(pivoted.df = nut.pivoted, 
                     var = 'nutrition_quality', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = savepath)

@@

plot_mean_comparison(pivoted.df = tobacco.pivoted, 
                     var = 'ncigs', 
                     group.var = 'scenario',
                     save = TRUE,
                     save.path = savepath)

@@

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'housing_quality',
                 save = TRUE,
                 save.path = savepath)
```

@@

cv_ordinal_plots(pivoted.df = nhsafe.pivoted, 
                 var = 'neighbourhood_safety',
                 save = TRUE,
                 save.path = savepath)
```

@@

cv_ordinal_plots(pivoted.df = lnly.pivoted, 
                 var = 'loneliness',
                 save = TRUE,
                 save.path = savepath)
```
